### 2022-08-10 main/chapter_2ljets.tex
first proofread of summaires section; add linking paragraph

\FloatBarrier
\subsection{Strong}
\label{sec:2ljets_origins_strong}
Strong supersymmetry, producing super-partners of quarks and gluons, would be
produced at much larger cross-sections than electroweak supersymmetry at the
LHC.
Squarks and gluinos are therefore excluded with masses up to several
$\eV[T]$ using hadronic data alone, depending on which simplified model is
considered~\cite{atlas_susy_strong_0l}.

The $\twoljets$-strong search targets strongly interacting supersymmetric
effects in cases where their decays produce pairs of charged leptons.
Like the RJR and electroweak $\twoljets$ searches, the $\twoljets$-strong
signals produce jets and invisible lightest supersymmetric particles.
Unlike the RJR and electroweak parts, not all of these leptons are produced
by $Z$ boson decays.
As illustrated in Figure~\ref{fig:2ljets_strong_signal_diagrams}, decay trees
featuring sleptons can also produce lepton pairs.
Lepton pairs produced in these slepton interactions are of the same flavour
and opposite charge, like those from $Z$ boson decays, but they have different
mass dilepton mass characteristics.

% signal models
\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_strong_gogo_qqqqllllN1N1_N2.pdf}
\caption{gluino-slepton}
\end{subfigure}
\hfill
\begin{subfigure}{0.47\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_strong_gogo_qqqqZZN1N1.pdf}
\caption{gluino-$Z^{(*)}$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_strong_sqsq_qqZZN1N1.pdf}
\caption{squark-$Z^{(*)}$}
\end{subfigure}
\caption[
Supersymmetric signal processes in the $\twoljets$-strong search
]{%
Supersymmetric signal processes in the $\twoljets$-strong search.
\emph{These figures are reproduced from the paper%
}~\cite{atlas2022searches, atlas_susy_feynman}.
\\[0.5em]
All models produce same-flavour, opposite-sign lepton pairs along with jets
and $\met$.
The gluino-slepton model (a) has a kinematic endpoint in $\mll$
given in Equation~\ref{eqn:2ljets_strong_max_mll}.
The gluino-$Z^{(*)}$ and squark-$Z^{(*)}$ models decay via $Z$ boson
resonances, which may be forced off-shell for small mass-splittings
$m(\neutralino_2) - m(\neutralino_1) < m(Z)$.
}
\label{fig:2ljets_strong_signal_diagrams}
\end{figure}

Rather than peaking at a resonance mass, these pairs have an $\mll$
distribution with a signature end-point which depends on the masses of other
supersymmetric particles in the
$\neutralino_2 \ldots \slepton \ldots \neutralino_1$
decay chain~\cite{paige1996determining}
\begin{equation}
\label{eqn:2ljets_strong_max_mll}
\max(\mll)
= m(\neutralino_2)
\sqrt{1 - \frac{m(\slepton\,)^2}{m(\neutralino_2)^2}}
\sqrt{1 - \frac{m(\neutralino_1)^2}{m(\slepton\,)^2}}
.
\end{equation}

Various previous incarnations of this search have been conducted with similar
selections and target models on in older data, including partial Run~2~\cite{
atlas_susy_strong_2l_partial_run2_1,
atlas_susy_strong_2l_partial_run2,
cms_susy_2016_strong_2l_run2_1,
cms_susy_2016_strong_2l_run2
} and Run~1~\cite{
atlas_susy_strong_2l_run1,
cms_susy_2016_strong_2l_run1
} in \atlas\ and \cms.
From these Run~1 searches, one can cherry-pick excesses
of ``$3.0$ standard deviations'' in \atlas\ \cite{atlas_susy_strong_2l_run1}
and ``$2.6$ standard deviations'' in \cms~\cite{cms_susy_2016_strong_2l_run1}.
These excesses of data above estimated backgrounds were not reproduced in their
early Run~2 updates.

% exclusion plots
\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_strong_contours_gluino_slepton.pdf}
\caption{gluino-slepton}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_strong_contours_gluino_z.pdf}
\caption{gluino-$Z^{(*)}$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_strong_contours_squark_z.pdf}
\caption{squark-$Z^{(*)}$}
\end{subfigure}
\caption[
Contours for signal models of the $\twoljets$-strong search
]{%
Contours for signal models of the $\twoljets$-strong search.
\emph{Figures were produced by the strong team%
}~\cite{atlas2022searches}.
\\[0.5em]
Each model point uses fit results from the signal region with the
``best expected sensitivity'';
jagged edges arise from the switching between contours set by these different
signal regions.
The grey shaded contours showing previous exclusion are taken
from~\cite{atlas_susy_strong_2l_partial_run2}.
}
\label{fig:2ljets_strong_contours}
\end{figure}

To target its signal models, $\twoljets$-strong search defines seven
overlapping signal regions.
Three target on-shell $Z^{(*)}$ models by selecting $\mll$ close to $m(Z)$,
and the others are binned in $\mll$ to give broad sensitivity to the various
kinematic edges across the grid of signal model parameters.

The largest Standard Model background to this search is dileptonic $\ttbar$,
in part because no $b$-jet veto is used.
All three signal models produce same-flavour lepton pairs, but $\ttbar$
produces same-flavour ($ee$/$\mu\mu$) and different-flavour ($e\mu$) pairs at
equal rates.
This difference in flavour symmetry is exploited to estimate backgrounds in
$\twoljets$-strong,
and its previous iterations~\cite{cms_susy_2016_strong_2l_run2_1}.
The estimate works by taking different-flavour data, weighting them by factors
to calibrate for differences in the leptons' reconstruction, and histogramming
them in same-flavour regions.
Simulations for $\ttbar$ and the smaller flavour symmetric backgrounds
$tW$, $WW$, and $\tau\tau$ are replaced by this estimate.

Post-fit results match the data to within $1$-sigma in all $\twoljets$-strong
regions.

Exclusion contours from the $\twoljets$-strong search are reproduced in
Figure~\ref{fig:2ljets_strong_contours}.
Besides their increased reach, the jagged edges to parts of these contour are
striking.
These arise from the combination of results from overlapping signal regions.
Because they overlap, they are not independent and cannot be trivially
combined.
Instead, each model in the signal grid is assigned to the signal region
with the ``best expected sensitivity'' by some measure.
An exclusion contour is constructed for each signal region, then those contours
are joined such that models assigned to each region use its corresponding
contour.

Personally, I find this hard to interpret.
If I had a pet theory which landed near to one of these sharp
region-transition edges, what should I make of these data?
Could some combination of the regions not have combined their information to
produce more precise contours?
Since model predictions change continuously, should our inferences not also?
To aid interpretations and to allow combinations of regions'
information, I chose to design the $\twoljets$-electroweak with only orthogonal
regions, and without any manual switching of regions between models.

\FloatBarrier
\subsection{Electroweak}
\label{sec:2ljets_origins_electroweak}
As motivated in the previous sections, I have personal preferences for
simulation-driven backgrounds and orthogonal multi-bin regions.
This is because simulation-driven estimates are interpretable as
Standard Model predictions,
and orthogonal regions have independent likelihoods which can be cleanly
combined to leverage the information in their data.

The main idea behind the design of the $\twoljets$-electroweak analysis is to
update the regions of the partial Run~2 search in its $\twoljets$
channel~\cite{atlas_23l_SUSY_2016_24}, which also searched for signal models
producing chargino-neutralino pairs which decay via $W$ and $Z$ bosons.
A particular goal was to improve sensitivity by replacing their overlapping
`SR2-int' and `SR2-high' regions with orthogonal selections.
\emph{Special thanks to Sarah~Williams for suggesting this approach.}

As in the $\twoljets$-strong search, the partial Run~2 search chose one
signal region from an expected sensitivity for each signal point,
as displayed in
Figure~\ref{fig:2ljets_23l_stuff}
with the two regions and exclusion contours.

@@

Additionally, $\twoljets$ widens its scope to target a GMSB simplified model
illustrated in Figure~\ref{fig:2ljets_signal_diagrams}.
The C1N2 and GMSB models behave similarly since both feature decays via massive
bosons ($W\kern-0.4exZ$, $ZZ$ or $Zh$) to leptons and jets, in similarly structures decay
trees to pairs of invisible supersymmetric particles.
Although widening sensitivity to both models does sacrifice sensitivity to
either one, the increased degree of model independence is itself of value for
future reinterpretations of the data.
We are happy to sacrifice some precision for generality.

Multi-bin fits are not special.
They are standard \atlas\ practice, and there could have been no complication
in replacing the overlapping SR2-int and SR2-high with orthogonally binned
regions.
However, my design decisions for $\twoljets$-electroweak
caused problems for the clarity of communication and accuracy of background
modelling.
These issues are developed further through the remainder of this chapter.

A multi-binned histogram is usually and clearly illustrated as slicing up one
variable.
My design of $\twoljets$-electroweak violates this.
Instead, it is designed as a tree whose branches recursively split various
variables.
This leads to specifications which are challenging to present and understand,
and which require region names with numerous suffixes to specify where they
live in that tree.

Worse, I disregarded the idea that every region should have a large
background expectation.
Normally, this is justified by the limitations of approximate statistical
methods, which work
``from as few as $\mathcal{O}(10)$ data events''~\cite{histfitter2014}.
But the Poisson likelihood works for infinitesimally small
expectations~\cite{skilling2009cosmology}, and in the small-bin limit one has
continuous distributions with Poisson normalizations
(sometimes called ``extended'' in high-energy
physics~\cite{barlow1990extended})
that are standard and easily analysed.

Events appearing in a region with minimal background is evidence in favour
of new contributions, and that only strengthens as the background approaches
zero.
For example, the top quark was observed by \dzero\ using seven regions all with
background expectations of $1$ or less, for a total of $3.79\pm0.55$ expected
and $17$ observed~\cite{abachi1995observation}.
If they could do that with technology from the year $1995$, we can do it now.

The real reason to avoid small backgrounds is, in this context, to allow honest
assignments of background uncertainties.
Although main simulated samples may have good precision,
many `systematic' variations and `data-driven' estimates are also required.
Many of these alternative estimates have far worse precision, and can fail
totally as the number of simulated events accepted plunges towards zero;
they can require $\approx10$ data events to work properly.

Unfortunately, $\twoljets$-electroweak selections were finalized before I
appreciated this problem that background variations were dubious.
Various workaround are invoked to assign plausible variations despite small
yields, which we shall in the remainder of this chapter.

As seen in the splash summary of Section~\ref{sec:2ljets_splash}, this search
finds agreement with backgrounds except for some local deficits of data below
backgrounds.
Exclusion contours exceed their expected range because of these deficits,
but they can only be trusted if the background model is trusted.

@@

For the C1N2 model, these public Run~2 \atlas\ searches explore the
all-hadronic~\cite{SUSY-2018-41},
$2/3\ell$ compressed~\cite{atlas_susy_compressed_2l_2018_run2},
$3\ell$ on-shell~\cite{SUSY-2018-06}, and
$3\ell$/same-sign~\cite{SUSY-2018-09} channels.
In comparison to these other searches, our exclusion contour of
Figure~\ref{fig:2ljets_contours_c1n2} excludes a unique area of parameter
space within $m(\chargino_1,\neutralino_2) \in 550\textrm{--}700\,\eV[G]$
and $m(\neutralino_1) \in 200\textrm{--}300\,\eV[G]$.
The all-hadronic search is most sensitive at the highest parent masses,
and three-lepton data of in the on-shell and compressed searches are most
sensitive at intermediate and small (off-shell/compressed) mass splittings.
For the GMSB model, our result complements limits from the
$4\ell$~\cite{SUSY-2018-02} and
all-hadronic~\cite{SUSY-2018-41} searches.
In addition to the exclusion contours that we present in
Figure~\ref{fig:2ljets_contours_gmsb}, the all-hadronic search again dominates
the heaviest parameter space, with $m(\neutralino_1) > 600\,\eV[G]$,
and the $4\ell$ search has more sensitivity at
$m(\neutralino_1) < 250\,\eV[G]$.
This leaves the area that our $\twoljets$-electroweak search uniquely excludes
to have with large Higgs branching fractions (up to $90\%$) at intermediate
masses with $m(\neutralino_1) \in 250\textrm{--}600\,\eV[G]$.

\section{Events}
\label{sec:2ljets_events}
This section describes the events selected for the $\twoljets$ searches, the
reconstructed particle objects derived from those events and various
important event variables.

>>>>

\FloatBarrier
\subsection{Strong}
\label{sec:2ljets_origins_strong}
Strong supersymmetry, producing super-partners of quarks and gluons, would be
produced at much larger cross-sections than electroweak supersymmetry at the
LHC.
Squarks and gluinos in simplified models are therefore excluded with masses up
to several $\eV[T]$ using hadronic data alone~\cite{atlas_susy_strong_0l}.

The $\twoljets$-strong search targets strongly interacting supersymmetric
effects in cases where their decays include pairs of charged leptons.
Like the RJR and electroweak $\twoljets$ searches, signal models targeted by
the $\twoljets$-strong search produce jets and invisible LSPs.
Unlike the RJR and electroweak parts, however, not all of these leptons are
produced by $Z$ boson decays;
as illustrated in Figure~\ref{fig:2ljets_strong_signal_diagrams}, decay trees
featuring sleptons can also produce lepton pairs.
Lepton pairs produced in these slepton interactions are of the same flavour
and opposite charge, like those from $Z$ boson decays, but they have different
mass dilepton mass characteristics.

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_strong_gogo_qqqqllllN1N1_N2.pdf}
\caption{gluino-slepton}
\end{subfigure}
\hfill
\begin{subfigure}{0.47\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_strong_gogo_qqqqZZN1N1.pdf}
\caption{gluino-$Z^{(*)}$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_strong_sqsq_qqZZN1N1.pdf}
\caption{squark-$Z^{(*)}$}
\end{subfigure}
\caption[
Diagrams for supersymmetric signal models targeted by the $\twoljets$-strong
search
]{%
Diagrams for supersymmetric signal models targeted by the $\twoljets$-strong
search.
\emph{These figures are reproduced from the paper%
}~\cite{atlas2022searches, atlas_susy_feynman}.
\\[0.5em]
All three produce same-flavour, opposite-sign lepton pairs along with jets
and $\met$.
The gluino-slepton model (a) has a kinematic endpoint in $\mll$
given in Equation~\ref{eqn:2ljets_strong_max_mll}.
The gluino-$Z^{(*)}$ and squark-$Z^{(*)}$ models decay via $Z$ boson
resonances that may be forced off-shell for small mass-splittings
$m(\neutralino_2) - m(\neutralino_1) < m(Z)$.
}
\label{fig:2ljets_strong_signal_diagrams}
\end{figure}

Rather than peaking at a resonance mass, the lepton pairs in the
`gluino-slepton' signal model have an $\mll$ distribution that features a
signature end-point that depends on the masses of other supersymmetric
particles in the
$\neutralino_2 \ldots \slepton \ldots \neutralino_1$
decay chain~\cite{paige1996determining}:
\begin{equation}
\label{eqn:2ljets_strong_max_mll}
\max(\mll)
= m(\neutralino_2)
\sqrt{1 - \frac{m(\slepton\,)^2}{m(\neutralino_2)^2}}
\sqrt{1 - \frac{m(\neutralino_1)^2}{m(\slepton\,)^2}}
.
\end{equation}

Previous incarnations of this search have been conducted with similar
selections and target models on in older data, including partial Run~2~\cite{
atlas_susy_strong_2l_partial_run2_1,
atlas_susy_strong_2l_partial_run2,
cms_susy_2016_strong_2l_run2_1,
cms_susy_2016_strong_2l_run2
} and Run~1~\cite{
atlas_susy_strong_2l_run1,
cms_susy_2016_strong_2l_run1
} in \atlas\ and \cms.
From these Run~1 searches, one can cherry-pick excesses
of ``$3.0$ standard deviations'' in \atlas\ \cite{atlas_susy_strong_2l_run1}
and ``$2.6$ standard deviations'' in \cms~\cite{cms_susy_2016_strong_2l_run1}.
These excesses of data above estimated backgrounds were not reproduced in their
early Run~2 updates.

To target its signal models, the $\twoljets$-strong search defines seven
overlapping signal regions.
Three target on-shell $Z^{(*)}$ models by selecting $\mll$ close to $m(Z)$,
and the others are binned in $\mll$ for sensitivity to the various
kinematic edges across the grid of signal model parameters.

The largest Standard Model background to this search is dileptonic $\ttbar$,
partly because no $b$-tagging veto is applied.
All three signal models produce same-flavour lepton pairs, but $\ttbar$
produces same-flavour ($ee$/$\mu\mu$) and different-flavour ($e\mu$) pairs at
equal rates ---
the $\twoljets$ search exploits this difference in flavour symmetry to derive
a data-driven background estimate for all of its flavour-symmetric backgrounds,
and have its previous iterations~\cite{cms_susy_2016_strong_2l_run2_1}.
The background estimate works by taking different-flavour data, weighting them
by factors to calibrate for differences in the leptons' reconstruction, and
histogramming them in same-flavour regions.
Simulations for $\ttbar$ and the smaller flavour symmetric backgrounds
$tW$, $WW$, and $\tau\tau$ are replaced by this estimate.

All post-fit results in $\twoljets$-strong regions match the data to within
$1$-sigma.

Exclusion contours from the $\twoljets$-strong search are reproduced in
Figure~\ref{fig:2ljets_strong_contours} and show a substantially increased
area of exclusion, improving by around $400\,\eV[G]$ in the largest limits on
$m(\tilde g)$ over the partial Run~2
results~\cite{atlas_susy_strong_2l_partial_run2}.
However, the jagged edges along these contour are striking.
This jaggedness arises from the method employed to combine exclusion contours
derived from individual signal regions.
Because they overlap, they are not independent and cannot be trivially
combined.
Instead, each model in the signal grid is assigned to the signal region
with the ``best expected sensitivity'' by some
measure~\cite{atlas2022searches}.
This combination method constructs an exclusion contour for each signal region,
then joins those contours such that models assigned to each region use its
corresponding contour.

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_strong_contours_gluino_slepton.pdf}
\caption{gluino-slepton}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_strong_contours_gluino_z.pdf}
\caption{gluino-$Z^{(*)}$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_strong_contours_squark_z.pdf}
\caption{squark-$Z^{(*)}$}
\end{subfigure}
\caption[
Contours for signal models of the $\twoljets$-strong search
]{%
Contours for signal models of the $\twoljets$-strong search.
\emph{These figures were produced by the strong team%
}~\cite{atlas2022searches}.
\\[0.5em]
Each model point uses fit results from the signal region with the
``best expected sensitivity'';
jagged edges arise from the switching between contours set by these different
signal regions.
The grey shaded contours showing previous exclusion are taken
from~\cite{atlas_susy_strong_2l_partial_run2}.
No previous contour is available for the exact squark-$Z^{(*)}$ model studied
here.
}
\label{fig:2ljets_strong_contours}
\end{figure}

Personally, I find these jagged contours hard to interpret.
If I had a pet theory that landed on one of these sharp
region-transition edges, what should I make of these data?
I wouldn't know.
It seems certain that some combination of the regions could have combined their
information to produce a continuous and more informative contour.
Where model predictions change continuously in these signal spaces, it seems
that our inferences should also.
To aid interpretations and to allow justifiable combinations of regions'
information, I therefore chose to design the $\twoljets$-electroweak with only
orthogonal regions, and without any switching of regions between models.

\FloatBarrier
\subsection{Electroweak}
\label{sec:2ljets_origins_electroweak}
As motivated in the previous sections, I have personal preferences for
simulation-driven backgrounds and orthogonal multi-bin regions.
Simulation-driven estimates are interpretable as Standard Model predictions,
relying less on loosely justified extrapolations,
and orthogonal regions have independent likelihood functions that can be
cleanly combined, by multiplication, to leverage the joint information in their
data.

The $\twoljets$-electroweak search aims to
update the regions of the partial Run~2 search in its $\twoljets$
channel~\cite{atlas_23l_SUSY_2016_24}, which also searched for the same C1N2
signal models that produce chargino-neutralino pairs decaying via $W$ and $Z$
bosons.
A particular design goal was to improve sensitivity by replacing their overlapping
`SR2-int' and `SR2-high' regions with orthogonal selections.
\emph{Special thanks to Sarah~Williams for suggesting this approach.}

Similarly to the $\twoljets$-strong search, the partial Run~2
search~\cite{atlas_23l_SUSY_2016_24} chose one signal region for each signal
point from a measure expected sensitivity measure and drew contours around
results from the chosen fit results.
The two signal regions SR2-int and SR2-high differ only by a selection of
$\met > 250\,\eV[G]$ and are displayed in Figure~\ref{fig:2ljets_23l_stuff},
along with the combined exclusion contour (additionally including an `SR2-low'
region and a three-lepton result) and the map of which region is chosen at
which signal point.

@@

Additionally, $\twoljets$ widens its scope to target a GMSB simplified model
illustrated in Figure~\ref{fig:2ljets_signal_diagrams}.
The C1N2 and GMSB models behave similarly since both feature gaugino decays via
massive bosons ($W\kern-0.4exZ$, $ZZ$ or $Zh$) to leptons and jets, in
similarly structures decay trees to invisible supersymmetric pairs.
Although widening sensitivity to both models must sacrifice some sensitivity to
each individually, the increased degree of model independence is itself of
value for future reinterpretations of our data.
We are happy to sacrifice some precision for generality.
Since the $W$ and $Z$ boson masses are similar, this sacrifice turns out to be
quite small anyway.

Multi-bin fits are not special.
They are standard \atlas\ practice, and there should have been no complication
had I designed copied SR2-int and SR2-high for $\twoljets$-electroweak but with
with minor tweaks to change them into orthogonally binned regions.
However, my design decisions for $\twoljets$-electroweak became much more
ambitious, increasing to a total of $13$ signal regions with complicated
definitions.
Although this multi-bin design squeezed out some extra sensitivity,
it also caused problems --- for the clarity of communication and the accuracy
of our background modelling;
these issues shall be developed throughout the remainder of this chapter.

A multi-binned histogram is usually and clearly illustrated as slicing up one
variable.
My design of $\twoljets$-electroweak violates this.
Instead, it is designed more like a tree whose branches recursively split
various variables.
This leads to specifications which are challenging to present or understand,
and which require region names with numerous suffixes to specify where they
live in that tree.

Worse, I disregarded the popular idea that every region should have a large
background expectation, preferably of ten events or more.
This requirement is typically justified by the limitations of approximate
statistical methods that work
``from as few as $\mathcal{O}(10)$ data events''~\cite{histfitter2014}.
But the Poisson likelihood works for infinitesimally small
expectations~\cite{skilling2009cosmology}, and in the small-bin limit one has
continuous distributions with Poisson normalizations
(sometimes called ``extended'' in high-energy
physics~\cite{barlow1990extended})
that are standard elsewhere in high energy physics, and are easily analysed
by the standard likelihood fitting methods.

Events appearing in a region with minimal background is evidence in favour
of new contributions, and that only strengthens as the background approaches
zero.
For example, the top quark was observed by \dzero\ using seven regions all with
background expectations of $1$ or less, for a total of $3.79\pm0.55$ expected
and $17$ observed~\cite{abachi1995observation}.
If they could do that with technology from the year $1995$, we can do it now.
This is a fact, but only if we can really trust our predictions of zero
backgrounds.

The real reason to avoid small backgrounds is, in this context, to allow honest
assignments of background uncertainties.
Although main simulated samples may have good precision,
many variations for systematic uncertainties and data-driven estimates are also
required.
Many methods to evaluate these variations have far worse precision than the
central simulations, and can fail totally as their number of Monte Carlo events
accepted plunges towards zero.
In practice, our methods to assign background uncertainties can easily require
tens of expected events to work properly.

Unfortunately, the $\twoljets$-electroweak regions designs were finalized
before unblinding and before I appreciated this problem with background
uncertainties in the smaller regions.
Various dubious workaround are invoked to assign plausible variations despite
small yields, which we shall in the remainder of this chapter.
As seen in the splash summary of Section~\ref{sec:2ljets_splash}, the
$\twoljets$-electroweak search observes agreement with post-fit backgrounds
except for some local deficits of data below backgrounds.
Exclusion contours exceed their expected range because of these deficits,
but they can only be trusted if the background model is trusted.

@@

For the C1N2 model, these public Run~2 \atlas\ searches explore the
all-hadronic~\cite{SUSY-2018-41},
$2/3\ell$ compressed~\cite{atlas_susy_compressed_2l_2018_run2},
$3\ell$ on-shell~\cite{SUSY-2018-06}, and
$3\ell$/same-sign~\cite{SUSY-2018-09} channels.
In comparison to these other searches, our exclusion contour of
Figure~\ref{fig:2ljets_contours_c1n2} excludes a unique area of parameter
space within $m(\chargino_1,\neutralino_2) \in 550\textrm{--}700\,\eV[G]$
and $m(\neutralino_1) \in 200\textrm{--}300\,\eV[G]$.
The all-hadronic search is most sensitive at the highest parent masses,
and three-lepton data of in the on-shell and compressed searches are most
sensitive at intermediate and small (off-shell/compressed) mass splittings.

For the GMSB model, our result complements limits from the
$4\ell$~\cite{SUSY-2018-02} and
all-hadronic~\cite{SUSY-2018-41} searches.
In addition to the exclusion contours that we present in
Figure~\ref{fig:2ljets_contours_gmsb}, the all-hadronic search again dominates
the heaviest parameter space, with $m(\neutralino_1) > 600\,\eV[G]$,
and the $4\ell$ search has more sensitivity at
$m(\neutralino_1) < 250\,\eV[G]$.
This leaves the area that our $\twoljets$-electroweak search uniquely excludes
to have with large Higgs branching fractions (up to $90\%$) at intermediate
masses with $m(\neutralino_1) \in 250\textrm{--}600\,\eV[G]$.
Exclusion of the largest $B(\neutralino_1 \rightarrow h \tilde{G})$ values
requires sensitivity to double-Higgs decay signatures --- \cms\ have published
exclusions in the region combining $hh\rightarrow \gamma\gamma+\met$ and
$hh\rightarrow b\bar bb\bar b$ with other channels to exclude
$B(\neutralino_1 \rightarrow h \tilde{G}) = 1$ up to
$m(\neutralino_1) = 750\,\eV[G]$~\cite{
cms_susy_2018_partial_run2_combination,
CMS-SUS-16-045,
CMS-SUS-16-044
}.

For reasons described in this section, the $\twoljets$-electroweak search is
designed with large number of orthogonal regions, and with those regions its
results offer some extensions over previous and orthogonal constraints.
Before describing those regions' definitions and modelling we apply to their
expected yields, the following sections now return to the basic details of the
data and event variables they use.

\section{Events}
\label{sec:2ljets_events}
This section describes the events selected for the three $\twoljets$ searches,
the reconstructed particle objects derived from those events and various
important event variables.
